---
title: "Final Project"
author: "Sohyun Lim"
date: "12-07-2024"
output: pdf_document
---

# 1. Load the data and fix the column names
```{r}
library(tidyverse)
library(ggplot2)
library(rvest)
library(stats)
library(rvest)
library(sentimentr)
library(tidytext)
library(sf)
library(stringr)
library(shiny)
library(dplyr)
library(shinyWidgets)

# Set the directory
setwd("/Users/sohyunlim/Desktop/R - final")

# Load the dataset
data <- read.csv("Public_Health_Statistics_-_Selected_public_health_indicators_by_Chicago_community_area_-_Historical_20241031.csv")

# Change column names
colnames(data) <- colnames(data) %>%
    tolower() %>%
    str_replace_all(fixed("."), "_") %>% 
    str_replace_all("__", "_") %>%
    str_replace("_$", "")   

# Select necessary columns
data <- data %>% select(community_area, community_area_name, 
                        cancer_all_sites, diabetes_related,
                        below_poverty_level, unemployment, per_capita_income)
```


# 2. Create a bar graph with top 10 community area by main variables

# 2-1. Public Health Indicator 
# a, cancer_all_sites : Mortality per 100,000 persons
# b. diabetes_related : Mortality per 100,000 persons
# 2-2. Socioeconomic Indicator
# a. below_poverty_level : Percent of households
# b. unemployment : Percent of persons in labor force aged 16 years and older
# c. per_capita_income : 2011 inflation-adjusted dollars

```{r}
# Create a table for cancer_all_sites
cancer_areas <- data %>%
  select(community_area, community_area_name, cancer_all_sites) %>%
  arrange(desc(cancer_all_sites))
top_10_cancer_areas <- head(cancer_areas, 10)

diabetes_areas <- data %>%
  select(community_area, community_area_name, diabetes_related) %>%
  arrange(desc(diabetes_related))
top_10_diabetes_areas <- head(diabetes_areas, 10)

poverty_areas <- data %>%
  select(community_area, community_area_name, below_poverty_level) %>%
  arrange(desc(below_poverty_level))
top_10_poverty_areas <- head(poverty_areas, 10)

umemployment_areas <- data %>%
  select(community_area, community_area_name, unemployment) %>%
  arrange(desc(unemployment))
top_10_umemployment_areas <- head(umemployment_areas, 10)

income_areas <- data %>%
  select(community_area, community_area_name, per_capita_income) %>%
  arrange(per_capita_income)
top_10_income_areas <- head(income_areas, 10)


# Create a bar chart
# 2-1_top_10_cancer.png
bar_cancer <- ggplot(top_10_cancer_areas, aes(x = reorder(community_area_name, cancer_all_sites), y = cancer_all_sites)) +
  geom_bar(stat = "identity", fill = "#377EB8") +
  coord_flip() +
  labs(
    title = "Top 10 Community Areas with Highest Cancer Mortality",
    x = "Community Area",
    y = "Cancer (Mortality per 100,000 persons)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.title.x = element_text(size = 12, face = "bold"),
    axis.title.y = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(size = 10, face = "bold"),
    axis.text.y = element_text(size = 10, face = "bold")
  )

bar_cancer

bar_cancer_path <- "/Users/sohyunlim/Desktop/R - final/pictures/2-1_top_10_cancer.png"
ggsave(bar_cancer_path, plot = bar_cancer, width = 8, height = 6, dpi = 300)

# 2-2_top_10_diabetes.png
bar_diabetes <- ggplot(top_10_diabetes_areas, aes(x = reorder(community_area_name, diabetes_related), y = diabetes_related)) +
  geom_bar(stat = "identity", fill = "#377EB8") +
  coord_flip() +
  labs(
    title = "Top 10 Community Areas with Highest Diabetes Mortality",
    x = "Community Area",
    y = "Diabetes (Mortality per 100,000 persons)"
  ) +
  theme_minimal() + 
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.title.x = element_text(size = 12, face = "bold"),
    axis.title.y = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(size = 10, face = "bold"),
    axis.text.y = element_text(size = 10, face = "bold")
  ) + 
  scale_y_continuous(
    limits = c(0, 130),  
    breaks = seq(0, 125, by = 25)  
  )

bar_diabetes

bar_diabetes_path <- "/Users/sohyunlim/Desktop/R - final/pictures/2-2_top_10_diabetes.png"
ggsave(bar_diabetes_path, plot = bar_diabetes, width = 11, height = 6, dpi = 300)

# 2-3_top_10_poverty.png
bar_poverty <- ggplot(top_10_poverty_areas, aes(x = reorder(community_area_name, below_poverty_level), y = below_poverty_level)) +
  geom_bar(stat = "identity", fill = "#377EB8") +
  coord_flip() +
  labs(
    title = "Top 10 Community Areas with Highest Poverty Level",
    x = "Community Area",
    y = "Poverty (%)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.title.x = element_text(size = 12, face = "bold"),
    axis.title.y = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(size = 10, face = "bold"),
    axis.text.y = element_text(size = 10, face = "bold")
  )

bar_poverty

bar_poverty_path <- "/Users/sohyunlim/Desktop/R - final/pictures/2-3_top_10_poverty.png"
ggsave(bar_poverty_path, plot = bar_poverty, width = 8, height = 6, dpi = 300)

# 2-4_top_10_unemployment.png
bar_unemployment <- ggplot(top_10_umemployment_areas, aes(x = reorder(community_area_name, unemployment), y = unemployment)) +
  geom_bar(stat = "identity", fill = "#377EB8") +
  coord_flip() +
  labs(
    title = "Top 10 Community Areas with Highest Unemployment",
    x = "Community Area",
    y = "Unemployment (%)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.title.x = element_text(size = 12, face = "bold"),
    axis.title.y = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(size = 10, face = "bold"),
    axis.text.y = element_text(size = 10, face = "bold")
  )

bar_unemployment

bar_unemployment_path <- "/Users/sohyunlim/Desktop/R - final/pictures/2-4_top_10_unemployment.png"
ggsave(bar_unemployment_path, plot = bar_unemployment, width = 8, height = 6, dpi = 300)

# 2-5_top_10_income.png
bar_income <- ggplot(top_10_income_areas, aes(x = reorder(community_area_name, -per_capita_income), y = per_capita_income)) +
  geom_bar(stat = "identity", fill = "#377EB8") +
  coord_flip() +
  labs(
    title = "Top 10 Community Areas with Lowest Income",
    x = "Community Area",
    y = "Income ($)"
  ) +
  theme_minimal() + 
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.title.x = element_text(size = 12, face = "bold"),
    axis.title.y = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(size = 10, face = "bold"),
    axis.text.y = element_text(size = 10, face = "bold")
  )

bar_income

bar_income_path <- "/Users/sohyunlim/Desktop/R - final/pictures/2-5_top_10_income.png"
ggsave(bar_income_path, plot = bar_income, width = 8, height = 6, dpi = 300)
```

# 3. Regression Model
# 3-1. Run a linear regression to study correlationship between socioeconomic factors and public health.

```{r}
# 3-1. below_poverty_level ~ cancer_all_sites
model_1 <- lm(cancer_all_sites ~ below_poverty_level, data = data)
summary(model_1)

# 3-2. unemployment ~ cancer_all_sites
model_2 <- lm(cancer_all_sites ~ unemployment, data = data)
summary(model_2)

# 3-3. per_capita_income ~ cancer_all_sites
model_3 <- lm(cancer_all_sites ~ per_capita_income, data = data)
summary(model_3)

# 3-4. below_poverty_level ~ diabetes_related
model_4 <- lm(diabetes_related ~ below_poverty_level, data = data)
summary(model_4)

# 3-5. unemployment ~ diabetes_related
model_5 <- lm(diabetes_related ~ unemployment, data = data)
summary(model_5)

# 3-6. per_capita_income ~ diabetes_related
model_6 <- lm(diabetes_related ~ per_capita_income, data = data)
summary(model_6)
```

# 3-2. Create scatter plots.
```{r}
# 3-1. below_poverty_level ~ cancer_all_sites
scatter_poverty_cancer <- ggplot(data, aes(x = below_poverty_level, y = cancer_all_sites)) +
  geom_point(color = "blue", size = 2) +  
  geom_smooth(method = "lm", color = "red", se = FALSE) +  
  labs(
    title = "Poverty Level and Cancer",
    x = "Below Poverty Level (%)",
    y = "Cancer (Mortality per 100,000 persons)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5)  
  )

scatter_poverty_cancer

scatter_poverty_cancer_path <- "/Users/sohyunlim/Desktop/R - final/pictures/3-1_scatter_poverty_cancer.png"
ggsave(scatter_poverty_cancer_path, plot = scatter_poverty_cancer, width = 8, height = 6, dpi = 300)

# 3-2. unemployment ~ cancer_all_sites
scatter_unemployment_cancer <- ggplot(data, aes(x = unemployment, y = cancer_all_sites)) +
  geom_point(color = "blue", size = 2) +  
  geom_smooth(method = "lm", color = "red", se = FALSE) +  
  labs(
    title = "Unemployment and Cancer",
    x = "Unemployment (%)",
    y = "Cancer (Mortality per 100,000 persons)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5)  
  )

scatter_unemployment_cancer

scatter_unemployment_cancer_path <- "/Users/sohyunlim/Desktop/R - final/pictures/3-2_scatter_unemplyoment_cancer.png"
ggsave(scatter_unemployment_cancer_path, plot = scatter_unemployment_cancer, width = 8, height = 6, dpi = 300)

# 3-3. per_capita_income ~ cancer_all_sites
scatter_income_cancer <- ggplot(data, aes(x = per_capita_income, y = cancer_all_sites)) +
  geom_point(color = "blue", size = 2) +  
  geom_smooth(method = "lm", color = "red", se = FALSE) +  
  labs(
    title = "Income and Cancer",
    x = "Income ($)",
    y = "Cancer (Mortality per 100,000 persons)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5)  
  )

scatter_income_cancer

scatter_income_cancer_path <- "/Users/sohyunlim/Desktop/R - final/pictures/3-3_scatter_income_cancer.png"
ggsave(scatter_income_cancer_path, plot = scatter_income_cancer, width = 8, height = 6, dpi = 300)

# 3-4. below_poverty_level ~ diabetes_related
scatter_poverty_diabetes <- ggplot(data, aes(x = below_poverty_level, y = diabetes_related)) +
  geom_point(color = "blue", size = 2) +  
  geom_smooth(method = "lm", color = "red", se = FALSE) +  
  labs(
    title = "Poverty Level and Diabetes",
    x = "Below Poverty Level (%)",
    y = "Diabetes (Mortality per 100,000 persons)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5)  
  )

scatter_poverty_diabetes

scatter_poverty_diabetes_path <- "/Users/sohyunlim/Desktop/R - final/pictures/3-4_scatter_poverty_diabetes.png"
ggsave(scatter_poverty_diabetes_path, plot = scatter_poverty_diabetes, width = 8, height = 6, dpi = 300)

# 3-5. unemployment ~ diabetes_related
scatter_unemployment_diabetes <- ggplot(data, aes(x = unemployment, y = diabetes_related)) +
  geom_point(color = "blue", size = 2) +  
  geom_smooth(method = "lm", color = "red", se = FALSE) +  
  labs(
    title = "Uemployment and Diabetes",
    x = "Uemployment (%)",
    y = "Diabetes (Mortality per 100,000 persons)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5)  
  )

scatter_unemployment_diabetes

scatter_unemployment_diabetes_path <- "/Users/sohyunlim/Desktop/R - final/pictures/3-5_scatter_unemployment_diabetes.png"
ggsave(scatter_unemployment_diabetes_path, plot = scatter_unemployment_diabetes, width = 8, height = 6, dpi = 300)

# 3-6. per_capita_income ~ diabetes_related
scatter_income_diabetes <- ggplot(data, aes(x = per_capita_income, y = diabetes_related)) +
  geom_point(color = "blue", size = 2) +  
  geom_smooth(method = "lm", color = "red", se = FALSE) +  
  labs(
    title = "Income and Diabetes",
    x = "Income ($)",
    y = "Diabetes (Mortality per 100,000 persons)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5)  
  )

scatter_income_diabetes

scatter_income_diabetes_path <- "/Users/sohyunlim/Desktop/R - final/pictures/3-6_scatter_income_diabetes.png"
ggsave(scatter_income_diabetes_path, plot = scatter_income_diabetes, width = 8, height = 6, dpi = 300)
```


# 4. Text Analysis
```{r}
# URL
url <- "https://www.cbsnews.com/chicago/news/cancer-care-disparities-1/"

# Load the web page and parse
page <- read_html(url)

# Extract the article content
article_section <- page %>%
  html_nodes(".content__body") %>%  
  html_text() %>%                   
  str_replace_all("\\s+", " ") %>%  
  str_squish()                      

# Save as txt. format.
file_path <- "/Users/sohyunlim/Desktop/R - final/text analysis/article_content.txt"  
cat(article_section, file = file_path, sep = "\n")
```

# 4-1. Sentimental analysis - article
```{r}
text_data <- article_section

# Analyze overall sentiment of the article
overall_sentiment <- sentiment(text_data)

# Calculate Polarity :  -0.04598272 (slightly negative)
polarity <- mean(overall_sentiment$sentiment)

# Calculate Subjectivity : 0.9540173 (relatively subject) 0~1
subjectivity <- 1 - abs(polarity)

# Print the Outcome
cat("Overall Polarity (Positive/Negative):", polarity, "\n")
cat("Overall Subjectivity (Objective/Subjective):", subjectivity, "\n")
```

# 4-2. Sentimental analysis - sentence
```{r}
text_data <- article_section

# Divide the article by sentence
sentences <- get_sentences(text_data)

# Run the sentimental analysis
sentiment_results <- sentiment(sentences)

# Check the outcome dataframe
head(sentiment_results)

# Arrange the data for visualization
plot_data <- sentiment_results %>%
  group_by(sentence_id) %>%
  summarise(sentiment = mean(sentiment))

# Add number to the sentence
plot_data$sentence_number <- seq_along(plot_data$sentence_id)

# Create a graph
sentence <- ggplot(plot_data, aes(x = sentence_number, y = sentiment)) +
  geom_line(color = "blue", size = 1) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +  
  labs(
    title = "Sentence Polarity of Article",
    x = "Sentence Number",
    y = "Polarity"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title.x = element_text(size = 12, face = "bold"),
    axis.title.y = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(size = 12, face = "bold"),
    axis.text.y = element_text(size = 12, face = "bold")
  )

sentence

sentence_path <- "/Users/sohyunlim/Desktop/R - final/text analysis/4-1_sentence_polarity_plot.png"
ggsave(filename = sentence_path, plot = sentence, width = 10, height = 6, dpi = 300)
```

# 4-3. Word frequency analysis - word
```{r}
# Convert text data into the dataframe format
text_df <- data.frame(text = article_section, stringsAsFactors = FALSE)

# Tokenize the text and remove stop words
custom_stopwords <- data.frame(word = c("said", "jones", "riggins", "thomas", "sinclair"), 
                               lexicon = "custom")
word_freq <- text_df %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words, by = "word") %>%
  anti_join(custom_stopwords, by = "word") %>%
  count(word, sort = TRUE)

# Check top 10 words
top_words <- head(word_freq, 10)
print(top_words)

# Create a bar graph with words frequency
word_frq <- ggplot(top_words, aes(x = reorder(word, n), y = n)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(
    title = "Top 10 Most Frequent Words",
    x = "Word",
    y = "Frequency"
  ) +
  theme_minimal() + 
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title.x = element_text(size = 12, face = "bold"),
    axis.title.y = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(size = 12, face = "bold"),
    axis.text.y = element_text(size = 12, face = "bold")         
  )

word_frq

word_frq_path <- "/Users/sohyunlim/Desktop/R - final/text analysis/4-2_word_frequency.png"
ggsave(filename = word_frq_path, plot = word_frq, width = 10, height = 6, dpi = 300)
```


# 5. Geospatial analysis
# Load a shp file.
```{r}
# Read csv file
healthcare_data <- read.csv("/Users/sohyunlim/Desktop/R - final/Map_-_Public_Health_Services_-_Chicago_Primary_Care_Community_Health_Centers.csv")

# Fix the column names
colnames(healthcare_data) <- colnames(healthcare_data) %>%
    tolower() %>%
    str_replace_all(fixed("."), "_") %>% 
    str_replace_all("__", "_") %>%
    str_replace("_$", "")   

head(healthcare_data)

# Extract latitude and longitude from Address
extract_lat_lon <- function(address) {
  match <- str_match(address, "\\(([-+]?[0-9]*\\.?[0-9]+), ([-+]?[0-9]*\\.?[0-9]+)\\)")
  if (!is.na(match[1, 1])) {
    return(c(as.numeric(match[1, 2]), as.numeric(match[1, 3])))
  } else {
    return(c(NA, NA))
  }
}

# Add latitude and longitude columns
lat_lon <- t(apply(as.data.frame(healthcare_data$address), 1, extract_lat_lon))
healthcare_data$latitude <- lat_lon[, 1]
healthcare_data$longitude <- lat_lon[, 2]

head(healthcare_data[, c("facility", "latitude", "longitude")])

# Drop NA 
healthcare_data <- healthcare_data %>% filter(!is.na(latitude) & !is.na(longitude))

# Convert into sf 
points_sf <- st_as_sf(
  healthcare_data,
  coords = c("longitude", "latitude"),
  crs = 4326  
)
```

```{r}
# Rad Shapefile 
chi_shp <- st_read("/Users/sohyunlim/Desktop/R - final/Comm_20Areas__1_/CommAreas.shp")
print(chi_shp)
```
# 5-1. Chicago Health Center Map
```{r}
# Check CRS
chi_shp <- st_transform(chi_shp, crs = 4326)
points_sf <- st_transform(points_sf, crs = 4326)

# Set the range of longitude and latitude of Chicago
chi_longitude_range <- c(-88, -87.5)  
chi_latitude_range <- c(41.6, 42)    

# Create a map
chicago_health_center <- ggplot() +
  geom_sf(data = chi_shp, fill = "lightgrey", color = "gray", alpha = 0.3) +  
  geom_sf(data = points_sf, color = "red", size = 2, shape = 21) +  
  labs(
    title = "Chicago Map with Healthcare Centers"
  ) +
  coord_sf(
    xlim = chi_longitude_range,  
    ylim = chi_latitude_range,  
    expand = FALSE
  ) +
  theme_void() +  
  theme(
    plot.title = element_text(
      hjust = 0.5,                
      size = 14,                  
      margin = margin(t = 10, b = 20)  
    )
  )

chicago_health_center

chicago_health_center_path <- "/Users/sohyunlim/Desktop/R - final/geospatial analysis/5-0_chicago_health_center.png"
ggsave(filename = chicago_health_center_path, plot = chicago_health_center, width = 10, height = 6, dpi = 300)
```

# Merge chicago shp and health dataset
```{r}
# Chicago shape file : chi_shp
# Chicago health dataset : data

# Fix the column names
colnames(chi_shp) <- colnames(chi_shp) %>%
    tolower() %>%
    str_replace_all(fixed("."), "_") %>% 
    str_replace_all("__", "_") %>%
    str_replace("_$", "")  

# Change column name in the shp file.
chi_shp <- chi_shp %>%
  rename(community_area = area_num_1)  

chi_shp$community_area <- as.numeric(chi_shp$community_area)
data$community_area <- as.numeric(data$community_area)

# Merge data
merged_data <- chi_shp %>%
  left_join(data, by = "community_area")
```

# 5-2. Chicago map with public health indicators
```{r}
# 1. cancer_all_sites
map_cancer <- ggplot(data = merged_data) +
  geom_sf(aes(fill = cancer_all_sites), color = "gray", size = 0.2) +
  scale_fill_gradient(
    low = "lightblue",
    high = "darkblue",
    name = "Cancer (Mortality per 100,000 persons)"
  ) +
  labs(
    title = "Cancer MOrtality in Chicago Community Areas"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.text = element_blank(),  
    axis.ticks = element_blank()
  )

map_cancer

map_cancer_path <- "/Users/sohyunlim/Desktop/R - final/geospatial analysis/5-1_chicago_cancer.png"
ggsave(filename = map_cancer_path, plot = map_cancer, width = 10, height = 6, dpi = 300)

# 2. diabetes_related
map_diabetes <- ggplot(data = merged_data) +
  geom_sf(aes(fill = diabetes_related), color = "gray", size = 0.2) +
  scale_fill_gradient(
    low = "lightblue",
    high = "darkblue",
    name = "Diabetes (Mortality per 100,000 persons)"
  ) +
  labs(
    title = "Diabetes Mortality in Chicago Community Areas"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.text = element_blank(),  
    axis.ticks = element_blank()
  )

map_diabetes

map_diabetes_path <- "/Users/sohyunlim/Desktop/R - final/geospatial analysis/5-2_chicago_diabetes.png"
ggsave(filename = map_diabetes_path, plot = map_diabetes, width = 10, height = 6, dpi = 300)
```

# 5-3. Chicago map with socioeconomic indicators
```{r}
# 3. below_poverty_level
map_poverty <- ggplot(data = merged_data) +
  geom_sf(aes(fill = below_poverty_level), color = "gray", size = 0.2) +
  scale_fill_gradient(
    low = "#FFF5B7",
    high = "red",
    name = "Poverty Level (%)"
  ) +
  labs(
    title = "Below Poverty Level by Chicago Community Areas"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.text = element_blank(),  
    axis.ticks = element_blank()
  )

map_poverty

map_poverty_path <- "/Users/sohyunlim/Desktop/R - final/geospatial analysis/5-3_chicago_poverty.png"
ggsave(filename = map_poverty_path, plot = map_poverty, width = 10, height = 6, dpi = 300)

# 4. unemployment
map_unemployment <- ggplot(data = merged_data) +
  geom_sf(aes(fill = unemployment), color = "gray", size = 0.2) +
  scale_fill_gradient(
    low = "#FFF5B7",
    high = "red",
    name = "Unemployment (%)"
  ) +
  labs(
    title = "Unemployment by Chicago Community Areas"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.text = element_blank(),  
    axis.ticks = element_blank()
  )

map_unemployment

map_unemployment_path <- "/Users/sohyunlim/Desktop/R - final/geospatial analysis/5-4_chicago_unemployment.png"
ggsave(filename = map_unemployment_path, plot = map_unemployment, width = 10, height = 6, dpi = 300)

# 5. per_capita_income
map_income <- ggplot(data = merged_data) +
  geom_sf(aes(fill = per_capita_income), color = "gray", size = 0.2) +
  scale_fill_gradient(
    low = "#FFF5B7",
    high = "#FF8040",
    name = "Income($)"
  ) +
  labs(
    title = "Income by Chicago Community Areas"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.text = element_blank(),  
    axis.ticks = element_blank()
  )

map_income

map_income_path <- "/Users/sohyunlim/Desktop/R - final/geospatial analysis/5-5_chicago_income.png"
ggsave(filename = map_income_path, plot = map_income, width = 10, height = 6, dpi = 300)
```


# 6. Shiny App

```{r}
# Convert CRS (EPSG:4326)
chi_shp <- st_transform(chi_shp, crs = 4326)
points_sf <- st_transform(points_sf, crs = 4326)
merged_data <- st_transform(merged_data, crs = 4326)

# Set the boundary of the map
chi_longitude_range <- c(-88, -87.5)
chi_latitude_range <- c(41.6, 42)

ui <- fluidPage(
    titlePanel("Chicago Public Health Indicators and Healthcare Centers"),
    sidebarLayout(
        sidebarPanel(
            selectInput(
                inputId = "variable",
                label = "Select Indicators to Display:",
                choices = c("Cancer Mortality" = "cancer_all_sites",
                            "Diabetes Mortality" = "diabetes_related",
                            "Below Poverty Level" = "below_poverty_level",
                            "Unemployment" = "unemployment",
                            "Per Capita Income" = "per_capita_income")
            ),
            switchInput(
                inputId = "show_healthcare",
                label = "Overlay Healthcare Centers",
                value = FALSE
            )
        ),
        mainPanel(
            plotOutput("map")
        )
    )
)

server <- function(input, output) {
    output$map <- renderPlot({
        selected_var <- input$variable
        show_healthcare <- input$show_healthcare

        base_map <- ggplot(data = merged_data) +
            geom_sf(aes_string(fill = selected_var), color = "gray", size = 0.2) +
            scale_fill_gradient(
                low = "lightblue",
                high = "darkblue",
                name = selected_var
            ) +
            labs(
                title = paste("Chicago Community Areas -", gsub("_", " ", selected_var))
            ) +
            coord_sf(
                xlim = chi_longitude_range,
                ylim = chi_latitude_range,
                expand = FALSE
            ) +
            theme_minimal() +
            theme(
                plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
                axis.text = element_blank(),
                axis.ticks = element_blank()
            )

        if (show_healthcare) {
    base_map <- base_map +
        geom_sf(data = points_sf, color = "red", size = 5, shape = 10) +
        coord_sf(
            xlim = chi_longitude_range,
            ylim = chi_latitude_range,
            expand = FALSE
        )
}

        base_map
    })
}

shinyApp(ui = ui, server = server)
```

# Additional. Create a map showing health outcome and socioeconomic status in Chicago
```{r}
# Top 10 regions overlapped regarding cancer and diabetes mortality
overlap_cancer_diabetes <- intersect(top_10_cancer_areas$community_area, top_10_diabetes_areas$community_area)

# Filter the data of those regions
overlap_data <- chi_shp %>% 
  filter(community_area %in% overlap_cancer_diabetes)

# Create a map
map_cancer_diabetes_overlap <- ggplot() +
  geom_sf(data = chi_shp, fill = "lightgrey", color = "gray", alpha = 0.3) + 
  geom_sf(data = overlap_data, fill = "red", color = "black", size = 0.2) +
  labs(
    title = "Top 10 Cancer & Diabetes Areas in Chicago"
  ) +
  theme_void() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold", margin = margin(t = 10, b = 20))
  )

map_cancer_diabetes_overlap

map_cancer_diabetes_overlap_path <- "/Users/sohyunlim/Desktop/R - final/pictures/2-6_top_10_overlap_health.png"
ggsave(map_cancer_diabetes_overlap_path, plot = map_cancer_diabetes_overlap, width = 8, height = 6, dpi = 300)


# Top 10 regions overlapped regarding highest poverty, unemplyoemtn, and low income
overlap_socioeconomic <- Reduce(intersect, list(
  top_10_poverty_areas$community_area,
  top_10_umemployment_areas$community_area,
  top_10_income_areas$community_area
))

# Filter the data of those regions
overlap_socioeconomic_data <- chi_shp %>% 
  filter(community_area %in% overlap_socioeconomic)

# Create a map
map_socioeconomic_overlap <- ggplot() +
  geom_sf(data = chi_shp, fill = "lightgrey", color = "gray", alpha = 0.3) + 
  geom_sf(data = overlap_socioeconomic_data, fill = "blue", color = "black", size = 0.2) +
  labs(
    title = "Top 10 Socioeconomic Indicators in Chicago"
  ) +
  theme_void() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold", margin = margin(t = 10, b = 20))
  )

map_socioeconomic_overlap

map_socioeconomic_overlap_path <- "/Users/sohyunlim/Desktop/R - final/pictures/2-7_top_10_overlap_socio.png"
ggsave(map_socioeconomic_overlap_path, plot = map_socioeconomic_overlap, width = 8, height = 6, dpi = 300)

```
